### 2019-08-28 manuscript_clean.Rmd
fleshed out readme

Table 2. Discriminant analysis of principal components for the presence of specific prey types using the morphological data. Top quartile variable (character) contributions to the linear discriminants are ordered from highest to lowest. Logistic regressions and GLMs were fitted to predict prey type presence and selectivity respectively. The sign of the slope of each predictor is reported, marked with an asterisk if significant, and highlighted grey if it differs between prey presence in diet and prey selectivity. green if significant (p value < 0.05). Pseudo-R^2^ (%) approximates the percent variance explained by the model.

>>>>

Table 2. Discriminant analysis of principal components for the presence of specific prey types using the morphological data. Top quartile variable (character) contributions to the linear discriminants are ordered from highest to lowest. Logistic regressions and GLMs were fitted to predict prey type presence and selectivity respectively. The sign of the slope of each predictor is reported, marked with an asterisk if significant (p value < 0.05), and highlighted grey if it differs between prey presence in diet and prey selectivity. Pseudo-R^2^ (%) approximates the percent variance explained by the model.
